Numerical simulation of the Cordilleran ice sheet \\ through the last glacial cycle

### 2014-07-09 kappa.tex
Re-update figure captions.

\begin{figure}
  \centering
  \makebox[0pt]{
    \subgraphics{a}{photo-glacier-crevasses}
    \hspace{1cm}
    \subgraphics{b}{photo-glacier-susitna}
    \hspace{1cm}
    \subgraphics{c}{photo-glacier-fold}
  }
  \caption{Illustration of various glacier ice behaviours.
           \textbf{(a)} Surface crevasses formed by ice flow over a hidden
           bedrock knob. Glacier Blanc, French Alps, 2004.
           \textbf{(b)} Medial moraines illustrating downhill ice flow on
           Susitna Glacier, Alaska Range, by Austin Post, 1970
           \citep{NSIDC.2009}.
           \textbf{(c)} Mountain glacier calving into a small lake, revealing a
           folded structure formed by deformed debris layers in the ice.
           Glacier d'Arsine, French Alps, 2004.}
  \label{fig:glacier-mechanics}
\end{figure}

\begin{figure}
  \centering
  \makebox[0pt]{
    \subgraphics{a}{photo-glacial-valley}
    \hspace{1cm}
    \subgraphics{b}{photo-erratic-boulder}
    \hspace{1cm}
    \subgraphics{c}{photo-melt-channels}
  }
  \caption{Different indicators of past glaciation.
           \textbf{(a)} Glacial valley, exhibiting a broad, U-shaped profile
           characteristic of erosion by glaciers.
           Cirque du Fer-\`{a}-Cheval, French Alps, 2013.
           \textbf{(b)} Erratic boulders, deposited in an improbable
           arrangement as the glacier melted underneath.
           Finse area, Norwegian Scandes, 2011.
           \textbf{(c)} Lateral meltwater channels, formed on a gentle slope
           as the ice margin retreated towards the valley bottom. Tuya Lake
           area, Canadian Cordillera, 2012.}
  \label{fig:glaciation-indicators}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=80mm]{paleo-glaciation}
  \caption{Spatial extent of ice sheet and glacier cover in the northern
           hemisphere \textbf{(a)} at present \citep{Patterson.Kelso.2014}, and
           \textbf{(b)} during the last glacial maximum
           \citep{Ehlers.Gibbard.2007}.}
  \label{fig:paleo-glaciation}
\end{figure}

@@

\begin{figure}
  \centering
  \makebox[0pt]{\includegraphics{photo-alaska-range}}
  \caption{The Alaska Range hosts several of the highest peaks in the North
           American Cordillera. Despite this fact and its northerly location,
           its north slope hosts relatively small glaciers only, which had not
           been much more extensive during the Last Glacial Maximum
           \citep{Kaufman.Manley.2004}, indicating dry climatic conditions.
           The Alaska Range is rapidly eroding, as shown by landslide-covered
           valley sides on this photograph.}
  \label{fig:photo-alaska-range}
\end{figure}

@@

\begin{figure}
  \centering
  \makebox[0pt]{
    \subgraphics{a}{photo-vancouver-island}
    \hspace{1cm}
    \subgraphics{b}{photo-fraser-valley}
  }
  \caption{Contrasted climates of the North American Cordillera.
           \textbf{(a)} Pacific Coast at Vancouver Island.
           \textbf{(b)} Fraser Valley, south-central British Columbia.}
  \label{fig:photo-fraser-valley}
\end{figure}

\begin{figure}
  \centering
  \makebox[0pt]{\includegraphics{plot-atm}}
  \caption{Some characteristics of the Cordilleran climate according to the
           North American Regional Reanalysis
           \citep[NARR,][]{Mesinger.etal.2006}}
  \label{fig:plot-atm}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=80mm]{model-interfaces}
  \caption{Model interfaces in PISM. From \citet{PISM-authors.2014}.
           \todo{Redraw.}}
  \label{fig:model-interfaces}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics{model-variables}
  \caption{Sketch of notations used for the main variables of the ice sheet
           model.}
  \label{fig:model-variables}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=80mm]{model-siassa}
  \caption{Shallow Ice Approximation (SIA) and Shallow Shelf Approximation
           (SSA) velocities in PISM. From \citet{Winkelmann.etal.2011}.
           \todo{Redraw.}}
  \label{fig:model-siassa}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=80mm]{model-pdd}
  \caption{PDD model. From \citet{PISM-authors.2014} \todo{Redraw.}}
  \label{fig:model-pdd}
\end{figure}

@@

\begin{figure}
  \centering
  \makebox[0pt]{\includegraphics{photo-tuya-moraine}}
  \caption{The Tuya Lake Moraine in northern British Columbia.}
  \label{fig:photo-tuya-moraine}
\end{figure}

>>>>

\begin{figure}
  \centering
  \makebox[0pt]{
    \subgraphics{a}{photo-glacier-crevasses}
    \hspace{1cm}
    \subgraphics{b}{photo-glacier-susitna}
    \hspace{1cm}
    \subgraphics{c}{photo-glacier-fold}
  }
  \caption{Illustration of various glacier ice behaviours:
           \textbf{(a)} surface crevasses formed by ice flow over a hidden
           bedrock knob, Glacier Blanc, French Alps, 2004;
           \textbf{(b)} medial moraines illustrating downhill ice flow on
           Susitna Glacier, Alaska Range, by Austin Post, 1970
           \citep{NSIDC.2009};
           \textbf{(c)} mountain glacier calving into a small lake, revealing a
           folded structure formed by deformed debris layers in the ice,
           Glacier d'Arsine, French Alps, 2004.}
  \label{fig:glacier-mechanics}
\end{figure}

\begin{figure}
  \centering
  \makebox[0pt]{
    \subgraphics{a}{photo-glacial-valley}
    \hspace{1cm}
    \subgraphics{b}{photo-erratic-boulder}
    \hspace{1cm}
    \subgraphics{c}{photo-melt-channels}
  }
  \caption{Different indicators of past glaciation:
           \textbf{(a)} glacial valley, exhibiting a broad, U-shaped profile
           characteristic of erosion by glaciers,
           Cirque du Fer-\`{a}-Cheval, French Alps, 2013;
           \textbf{(b)} erratic boulders, deposited in an improbable
           configuration as the glacier melted underneath,
           Finse area, Norwegian Scandes, 2011;
           \textbf{(c)} lateral meltwater channels, formed on a gentle slope
           as the ice margin retreated towards the valley bottom, Tuya Lake
           area, Canadian Cordillera, 2012.}
  \label{fig:glaciation-indicators}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=80mm]{paleo-glaciation}
  \caption{Spatial extent of ice sheet and glacier cover in the northern
           hemisphere \textbf{(a)} at present \citep{Patterson.Kelso.2014}, and
           \textbf{(b)} during the last glacial maximum
           \citep{Ehlers.Gibbard.2007}.
           \todo{Make these globes look a little bigger. Add (a) and (b).}}
  \label{fig:paleo-glaciation}
\end{figure}

@@

\begin{figure}
  \centering
  \makebox[0pt]{\includegraphics{photo-alaska-range}}
  \caption{The Alaska Range hosts several of the highest peaks in the North
           American Cordillera. Despite this fact and its northerly location,
           its north slope hosts relatively small glaciers only, which had not
           been much more extensive during the Last Glacial Maximum
           \citep{Kaufman.Manley.2004}, indicating dry climatic conditions.
           The Alaska Range is tectonically active and rapidly eroding, as
           shown by landslide-covered valley sides on this photograph.}
  \label{fig:photo-alaska-range}
\end{figure}

@@

\begin{figure}
  \centering
  \makebox[0pt]{
    \subgraphics{a}{photo-vancouver-island}
    \hspace{1cm}
    \subgraphics{b}{photo-fraser-valley}
  }
  \caption{Contrasted climates of the North American Cordillera:
           \textbf{(a)} Pacific Coast at Vancouver Island, western British
           Columbia, by Martin Margold, 2010.
           \textbf{(b)} Fraser Valley, south-central British Columbia, 2010.}
  \label{fig:photo-fraser-valley}
\end{figure}

\begin{figure}
  \centering
  \makebox[0pt]{\includegraphics{plot-atm}}
  \caption{Some characteristics of the Cordilleran climate according to the
           North American Regional Reanalysis
           \citep[NARR,][]{Mesinger.etal.2006}.}
  \label{fig:plot-atm}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=80mm]{model-interfaces}
  \caption{Model interfaces in PISM. From \citet{PISM-authors.2014}.
           \todo{This is directly from the PISM manual. I may redraw it here
                 if I have the time.}}
  \label{fig:model-interfaces}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics{model-variables}
  \caption{Sketch of notations used for the main variables of the ice sheet
           model. A particle of ice is moving at velocity $\vv$, under the
           balance of stresses $\CST$ and gravity $\vect{g}$.}
  \label{fig:model-variables}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=80mm]{model-siassa}
  \caption{Shallow Ice Approximation (SIA) and Shallow Shelf Approximation
           (SSA) velocities in PISM. From \citet{Winkelmann.etal.2011}.
           \todo{Redraw in LaTeX in the same style as
                 \cref{fig:model-variables}.}}
  \label{fig:model-siassa}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{model-pdd}
  \caption{PDD model. From \citet{PISM-authors.2014}
           \todo{This is again directly from the PISM manual. I can simplify
                 it by removing the unused refreezing branch, I will match
                 notations with the text and refer to equations in use.}}
  \label{fig:model-pdd}
\end{figure}

@@

%\begin{figure}
%  \centering
%  \makebox[0pt]{\includegraphics{photo-tuya-moraine}}
%  \caption{The Tuya Lake Moraine in northern British Columbia.}
%  \label{fig:photo-tuya-moraine}
%\end{figure}
